Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-03-04 analysis/paper/paper.Rmd
start table for long labels on contribution plot

>>>>

long_labels <- 
  tribble(       ~long_labels,             ~short_labels, 
                 "X Value: Top Left",         "1.X",
                 "Y Value: Top Left",         "2.X",
                 "X Value: Mid-Upper Left",    "...",
                 "Y Value: Mid-Upper Left",    
                 "X Value: Mid-Lower Left",    
                 "Y Value: Mid-Lower Left",    
                 "X Value: Bottom Left",      
                 "Y Value: Bottom Left",      
                 "X Value: Distal Tip",        
                 "Y Value: Distal Tip",       
                 "X Value: Bottom Right",     
                 "Y Value: Bottom Right",     
                 "X Value: Mid-Lower Right",   
                 "Y Value: Mid-Lower Right",    
                 "X Value: Mid-Upper Right",    
                 "Y Value: Mid-Upper Right",    
                 "X Value: Top Right",          
                 "Y Value: Top Right",           
                 )
